Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations

### 2023-08-11 index.qmd
update authors

---
title: Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations
authors:
  - name: Tanya Strydom
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0001-6067-1349
    email: tanya.strydom@umontreal.ca
  - name: Salomé Bouskila
    affiliation:
        - ref: udem
    roles: writing
    corresponding: false
    orcid: 0000-0003-0193-5441
    email: salome.bouskila@umontreal.ca
  - name: Francis Banville
    affiliation:
        - ref: udem
        - ref: qcbs
        - ref: udes
    orcid: 0000-0001-9051-0597
    email: francis.banville@umontreal.ca
  - name: Ceres Barros
    affiliation:
        - Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
    orcid: 0000-0003-4036-977X
    email: cbarros@mail.ubc.ca
affiliations:
    - id: udem
      name: Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
    - id: qcbs
      name: Québec Centre for Biodiversity Science, Montréal, Canada
    - id: udes
      name: Département de Biologie, Université de Sherbrooke, Sherbrooke, Canada
bibliography: references.bib
---

>>>>

---
title: Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations
authors:
  - name: Tanya Strydom
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0001-6067-1349
    email: tanya.strydom@umontreal.ca
  - name: Salomé Bouskila
    affiliation:
        - ref: udem
    roles: writing
    corresponding: false
    orcid: 0000-0003-0193-5441
    email: salome.bouskila@umontreal.ca
  - name: Francis Banville
    affiliation:
        - ref: udem
        - ref: qcbs
        - ref: udes
    orcid: 0000-0001-9051-0597
    email: francis.banville@umontreal.ca
  - name: Ceres Barros
    affiliation:
        - ref: ubcforest
    orcid: 0000-0003-4036-977X
    email: cbarros@mail.ubc.ca
  - name: Dominique Caron
    affiliation:
        - ref: mcgill
        - ref: qcbs
    orcid: 0000-0002-2151-6693
    email: dominique.caron@mail.mcgill.ca
  - name: Maxwell J. Farrell
    affiliation:
        - ref: uoft
    orcid: 0000-0003-0452-6993
    email: maxwell.farrell@utoronto.ca
  - name: Marie-Josée Fortin
    affiliation:
        - ref: uoft
    orcid: 0000-0002-9935-1366
    email: mariejosee.fortin@utoronto.ca
  - name: Victoria Hemming
    affiliation:
        - ref: ubccons
    orcid: 0000-0003-3220-6161
    email: victoria.hemming@ubc.ca
  - name: Benjamin Mercier
    affiliation:
        - ref: udes
        - ref: qcbs
    orcid: 0000-0002-4104-9463
    email: benjamin.b.mercier@usherbrooke.ca
  - name: Laura J. Pollock
    affiliation:
        - ref: mcgill
        - ref: qcbs
    orcid: 0000-0002-6004-4027
    email: laura.pollock@mcgill.ca
  - name: Rogini Runghen
    affiliation:
        - ref: ucecology
    orcid: 0000-0001-5785-8321
    email: rogini.runghen@gmail.com
  - name: Giulio V. Dalla Riva
    affiliation:
        - ref: ucmath
    orcid: 0000-0002-3454-0633
    email: giulio.dallariva@canterbury.ac.nz
  - name: Timothée Poisot
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0002-0735-5184
    corresponding: true
    email: timothee.poisot@umontreal.ca
affiliations:
    - id: udem
      name: Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
    - id: qcbs
      name: Québec Centre for Biodiversity Science, Montréal, Canada
    - id: udes
      name: Département de Biologie, Université de Sherbrooke, Sherbrooke, Canada
    - id: ubcforest
      name: Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
    - id: mcgill
      name: Department of Biology, McGill University, Montréal, Canada
    - id: uoft
      name: Department of Ecology & Evolutionary Biology, University of Toronto, Toronto, Canada
    - id: ubccons
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
    - id: ucecology
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
    - id: ucmath
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
bibliography: references.bib
---
